PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-05-23 qfenv_paper/qf_environment.tex
edits on the paper

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \gon {Gonz\'{a}lez}
\def \Hbp {H$\beta ^\prime$}

@@

\title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}

\begin{abstract}
We present the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
different density environments from $z=0.0$ to $0.8$ using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
a stellar mass limited galaxy population of 
$\sim 40000$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $\sim 100000$
galaxies from SDSS within redshift range $0.0375-0.145$. Using an evolving cut based on
specific star formation, we classify the galaxies as quiescent or star-forming and
measure its environment using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} we construct 
from PRIMUS and SDSS. Based on its environment we classify our target
population into dense or sparse environments.

With the target galaxy population divided into quiescent and star-forming galaxies 
in dense and sparse environments, we calculate the stellar mass functions 
(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
$z=0.8$ to $0.0$ for both high and low environments. 
In addition, throughout the redshift range the difference between the
$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
is independent of environment. 
\end{abstract}

>>>>

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}

@@

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}

\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS). We examine the stellar mass function (SMF) evolution for each of our subsamples of quiescent and star-forming galaxies in low and high density environments. We find, from the $f_{\rm{Q}}(\mathcal{M}_{*})$ computed from these SMFs, that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range. Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range. These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.  
\end{abstract}
